\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Full-Stack Software Engineer}{Feb 2023 - Present}
{Geisel Software}{Worcester, MA}
\resumeItemListStart
\resumeItem{
  Scoped requirements directly with stakeholders and owned delivery from design
  through production across multiple client engagements.
}
\resumeItem{
  Rebuilt CI/CD for AI-assisted development velocity: trunk-based workflow,
  CalVer releases, staging-to-prod promotion, per-environment rebuilds from
  pinned SHAs, automated smoke tests on ECS Fargate.
}
\resumeItem{
  Onboarded engineers onto active projects, establishing architectural patterns,
  documentation, and review standards to accelerate ramp-up.
}
\resumeItemListEnd

\resumeClientHeading
{Client: Valinor Technologies, Deployable Medical System (HarborOS)}
{Co-Architect}
{Defense / Healthcare}
\resumeItemListStart
\resumeItem{
  Co-architected the full software stack for a containerized mobile medical bay
  with telehealth, patient monitoring, remote device control, and offline-first
  medical resources; delivered prototypes to U.S. Marine Corps and special
  operations forces.
}
\resumeItem{
  Guided the product through FedSTART certification for federal deployment while
  expanding the feature set under aggressive timelines.
}
\resumeItem{
  Integrated multiple proprietary medical devices without hardware access until
  final stages, designing abstraction layers that enabled rapid integration once
  hardware arrived.
}
\resumeItemListEnd

\resumeClientHeading
{Client: Amazon Robotics, Serverless Data Platform}
{Full-Stack Engineer}
{Robotics R\&D}
\resumeItemListStart
\resumeItem{
  Shipped features and performance optimizations for the primary data discovery,
  visualization, and troubleshooting tool used by robotics engineers across
  multiple programs, serving 15K+ requests/month.
}
\resumeItem{
  Built interactive 3D visualizations (point clouds, video overlays, spatial
  telemetry) enabling R\&D debugging of robotic warehouse automation.
}
\resumeItem{
  Engineered a data indexing solution achieving a 50x reduction in load times.
}
\resumeItemListEnd

\resumeSubheading
{Embedded / Full-Stack Software Engineer}{Aug 2021 - Feb 2023}
{General Dynamics Mission Systems}{Dedham, MA}
\resumeItemListStart
\resumeItem{
  Delivered a hybrid embedded + web system on a 5-person cross-disciplinary IRAD
  team spanning systems, embedded, and security.
}
\resumeItem{
  Implemented a React-based management interface, owning the full integration
  path between hardware and UI.
}
\resumeItem{
  Earned direct mentorship from the company President through consistent
  contribution to product and business strategy beyond engineering scope.
}
\resumeItemListEnd

\resumeSubHeadingListEnd
